As I am sitting in my home, finishing up the thesis, during these unusual time of a global pandemic, I want to thank first to all front-line healthcare and essential workers all over the world.

I would like to thank my advisors and mentors: Daniele have provided constant support over the six years, guiding me the growth from fresh college graduate to familiar with methodological thinking. And Denis, thanks for teaching me judging good research and mathematical rigor, also being an academic role model. Teseo, thanks for always listening and participating in my constant debate from tiny details to research directions, regardless of the time of the day.
I would also express my gratitude to the committee members of this thesis, it is great to have you during the milestone of my PhD studies, Ken from Depth Qualification Exam and Georg from my thesis proposal.

I am fortunate to have many academic collaborators from whom I learn from, not all chatting becomes a research project and not all project yeilds visible output, but each interaction makes a dent to the way we move forward. And the thesis wouldn't be the same without all these experiences:
Ligang for leading me to the fascinating field of geometry processing;
Scott for helping me through the very first project in my research journey;
Joan and Ilya for teaching me some of the basic theory in learning;
Anna, Albert, Francis, Alexey, Evgeny, Marc for collaborating towards processing the large dataset;
Junior, Tiantian, Ladislav for teaching me animation, and showing me around in Utah campus;
Minjie, Lingfan, Jinyang for setting a good taste on systems design; 
Davi, Julian, Chase and Zach for getting my hands dirty on 3D printing and laser cutting machines, and see how digital can be connected to real objects that I can touch;
Jeremie and Xifeng for participating on various discussions and long lasting impact in my career;
Hanxiao for walking through the realm of parameterization together;
Yixin for establishing the calaber in the lab
Qingnan, Ziyi, Yixin, YunFan, JiaCheng
Ladislav, Jinyang, Lingfan, Vova, Marc, Xifeng, 

During my various internships, Vova: thank you for providing generous support during my internship at Adobe over a year. 
Suraj: thank you for the support at nTopology. 
\begin{itemize}
  \item nTopology Inc, Suraj, support.
  \item Labmates: Francisca, Chase, Julian, Qingnan, Davi, Jeremie, BoLun, Anna Koch, Zizhou,
  \item Officemates: Junbo Z, Xiang Z, Xifeng G
  \item Staff: Shenglong, Hong Tam.
  \item Friends: Wenjun, Yueteng, Yishuai, Wenshuo, Han, Cheng, Yixin Tao
\end{itemize}

Finally, I would like to thank my Mom and Dad for believing in me and being supportive of my choices far from home. And my thanks go to Run, my muse and inspiration, for always by my side through ups and downs.